\documentclass[12pt,a4paper,oneside]{article}

\usepackage[margin=3cm]{geometry}

\usepackage{hyperref}
\hypersetup{
    pdftitle={COM 388, Introduction to Web Programming},%
    pdfauthor={Toksaitov Dmitrii Alexandrovich},%
    pdfsubject={Syllabus},%
    pdfkeywords={COM;}{388;}{syllabus;}{introduction;}{web;}{programming},%
    colorlinks,%
    linkcolor=black,%
    citecolor=black,%
    filecolor=black,%
    urlcolor=black
}

\newcommand{\R}[1]{\uppercase\expandafter{\romannumeral #1\relax}}

\begin{document}

    \title{COM 388, Introduction to Web Programming}
    \author{
        American University of Central Asia\\
        Software Engineering Department
    }
    \date{}
    \maketitle

    \section{Course Information}

        \begin{description}
            \item[Course ID]\hfill\\
                COM 388, 2805, 3040
            \item[Course Repositories]\hfill\\
                \url{https://github.com/auca/com.388}
            \item[Place]\hfill\\
                AUCA, laboratory G31
            \item[Time]\hfill\\
                Tuesday 10:50\\
                Thursday 10:50
        \end{description}

    \section{Prerequisites}

        COM 112, Programming \R{2}

    \section{Contact Information}

        \begin{description}
            \item[Instructor]\hfill\\
                Toksaitov Dmitrii Alexandrovich\\
                \href{mailto:toksaitov_d@auca.kg}{toksaitov\_d@auca.kg}
            \item[Office]\hfill\\
                AUCA, Room 315\\
                AUCA, Media Laboratory
            \item[Office Hours]\hfill\\
                Monday 12:45--17:00\\
                Tuesday 15:35--17:00\\
                Thursday 12:45--17:00\\
                Friday 12:45--17:00
        \end{description}

    \section{Course Overview}

        This course teaches students to master tools and techniques to develop
        web applications. Students will study basic networking concepts focusing
        on The Hypertext Transfer Protocol (HTTP), the foundation of data
        communication for the World Wide Web. Students will learn the HyperText
        Markup Language (HTML) and Cascading Style Sheets (CSS) to describe and
        style content of their web documents. The course introduces students to
        the JavaScript programming language for both front-end and back-end
        development with a brief introduction to other popular languages,
        environments, and frameworks. Last but not least, students will take a
        look on how to configure a web server, work with relational and
        non-relational databases, scale their sites, and use cloud services.

    \section{Topics Covered}

        \begin{itemize}
            \item Preparing a development environment
            \item Network fundamentals
            \item The HyperText Markup Language
            \item Cascading Style Sheets
            \item The JavaScript programming language and the Node.js runtime
            \item Relational and non-relational databases
            \item Authorization, authentication and security
            \item Caching and scaling up
            \item Containerization
            \item Publishing web applications
            \item Cloud services
        \end{itemize}

    \section{Practice Tasks \& Quizzes}

        Students are required to finish 4 practice tasks. The tasks are based on
        topics discussed during lectures. Each task should be finished during
        the class to receive a grade.

        Students will get four quizzes throughout the course on topics discussed
        during classes.

    \section{Course Project}

        Students will take one course project to develop a web application for
        an imaginary customer. Students are free to select languages,
        frameworks, database systems, and other tools they like or would like to
        try.

    \section{Reading}

        \begin{enumerate}
            \item HTML \& XHTML: The Definitive Guide, 6th Edition by Chuck
            Musciano, Bill Kennedy (ISBN: 978-0596527327)
            \item CSS: The Definitive Guide, 3rd Edition by Eric A. Meyer (ISBN:
            978-0596527334)
            \item JavaScript: The Definitive Guide: Activate Your Web Pages by
            David Flanagan (ISBN: 978-0596805524)
            \item JavaScript: The Good Parts by Douglas Crockford (ISBN:
            978-0596517748)
        \end{enumerate}

        \subsection{Supplemental Reading}

            \begin{enumerate}
                \item Design Patterns: Elements of Reusable Object-Oriented
                Software by Erich Gamma, Richard Helm, Ralph Johnson, John
                Vlissides (AUCA Library Call Number: QA 76.64 D47 1995, ISBN:
                978-0201633610)
                \item Refactoring: Improving the Design of Existing Code by
                Martin Fowler, Kent Beck, John Brant, William Opdyke, Don
                Roberts (AUCA Library Call Number: QA76.76.R42 F695 1999, ISBN:
                978-0201485677)
            \end{enumerate}

    \section{Grading}

        \begin{itemize}
            \item Practice tasks (30\%)
            \item Quizzes (20\%)
            \item Course project (50\%)
        \end{itemize}

        \begin{itemize} \itemsep-10pt \parskip0pt \parsep0pt
            \item[--] 90\%--100\%: A\\
            \item[--] 80\%--89\%: A-\\
            \item[--] 70\%--79\%: B+\\
            \item[--] 65\%--69\%: B\\
            \item[--] 60\%--64\%: B-\\
            \item[--] 56\%--59\%: C+\\
            \item[--] 53\%--55\%: C\\
            \item[--] 50\%--52\%: C-\\
            \item[--] 46\%--49\%: D+\\
            \item[--] 43\%--45\%: D\\
            \item[--] 40\%--42\%: D-\\
            \item[--] Less than 39\%: F
        \end{itemize}

    \section{Rules}

        Students are required to follow the rules of conduct of the Software
        Engineering Department and American University of Central Asia.

        Team work is NOT encouraged. Equal blocks of code or similar structural
        pieces in separate works will be considered as academic dishonesty and
        all parties will get zero for the task.

\end{document}

